### 2023-04-28 application.tex
up

 \\ \hline
   RP  
   	& Decidable (Thm~\ref{down-up})  
   		 & Decidable (Thm~\ref{up-down})

    \\ \hline
   BRP  
   &  Decidable (Thm~\ref{down-up}) 
   		 & ??

    \\ \hline
      kRP  
      & Decidable (Thm~\ref{down-up}) 
      		& ??

       \\ \hline
   sRP  
   	& Decidable (Thm~\ref{post srp})
   		 & Decidable (Thm~\ref{downward srp})

@@

>>>>

 \\ \hline
   RP  
   	& Decidable (Thm~\ref{down-up})  
   		 & ??

    \\ \hline
   BRP  
   &  Decidable (Thm~\ref{down-up}) 
   		 & Decidable (never hold ?)

    \\ \hline
      kRP  
      & Decidable (Thm~\ref{down-up}) 
      		& Decidable (never hold ?)

       \\ \hline
   sRP  
   	& Decidable (Thm~\ref{post srp})
   		 & ??

@@

\begin{proposition}
{\sc Bounded resilience} and {\sc $k$-resilience} never hold for vector addition system when $\Safe = \downarrow \Safe$ and $\Bad = \uparrow \Bad$
\end{proposition}

\begin{proof}
Consider a given $k \in \N$.
Consider $\Bad \subseteq \N^d$ upward-closed and $\Safe \subseteq \N^d$ downward-closed.
Consider a given Vector addition system, which has a finite number of transitions.
Let us call $c_{\max}$ the maximal constant in a coordinate of a transition.

$\Bad$ admits a finite basis $B_\Bad$.
Consider $\textbf{v}_k$ obtained by summing all members of the basis of $\Bad$ and then consider 
$\textbf{u}_k = \textbf{v}_k + (k+1) \cdot (c_{\max}, c_{\max}, \ldots, c_{\max})$.

All configurations reachable from $\textbf{u}_k$ in $k$ or less steps are above $ \textbf{v}_k $
and thus, are in $\Bad$, by upward-closedness.

Hence  $\Safe$ is not reachable from $\textbf{u}_k$ in $k$ or less steps  and {$k$-resilience} does not hold.
Since the reasoning hold for all $k \in \N$, {\sc Bounded-resilience} does not hold.
\end{proof}

\mathieu{
En train d'essayer de réfléchir voir si ça s'adapte aussi aux VASS.}

### 2023-04-28 state-resilience.tex
up

\begin{proof}
Consider Reset $d$-VASS
with $\Safe$ % where  $ \textbf{0} = 0^d \in \mathbb{N}^d$ 
	containing only the
		configurations in $Q \times \{ \textbf{0} \}$
	where $\textbf{0} = \min(\mathbb{N}^d)$, %$0$ 
% \alain{tu n'as pas le doit d'écrire $0$ sans explication}
and $\Bad = \mathbb{N}^d \setminus \Safe$.
It follows in this case that
{\sc State-resilience} 
% \alain{écris toujours pareil les expressions choisies comme state-resilience}
is equivalent 
to the problem of whether 
% $0$  can be visited infinitely often. 
it is possible to visit infinitely often configurations with every vector having all values equal to $0$.
% \alain{incompréhensible, explique}
Indeed, from such a configuration, then the next step is either also such a configuration, either it is in $\Bad$, in which case, we know it is possible to reach such a configuration again. From this we know there exists a sequence 
$(q_i ({\textbf{v}_{i}}) )_{i\in\N}$ 
such that for all $i\in\N$ 
$\exists j \in \N$, $j>i$, s.t. ${\textbf{v}_j} = \textbf{0}$.
% Since reachability of $0$ is undecidable for Reset VASS, we conclude.
Hence the undecidability.
\end{proof}

>>>>

\begin{proof}
Consider Reset $d$-VASS
with $\Safe$ % where  $ \textbf{0} = 0^d \in \mathbb{N}^d$ 
	containing only the
		configurations in $Q \times \{ \textbf{0} \}$
	where $\textbf{0} = \min(\mathbb{N}^d)$, %$0$ 
% \alain{tu n'as pas le doit d'écrire $0$ sans explication}
and $\Bad = \mathbb{N}^d \setminus \Safe$.

\mathieu{refaire la preuve}
\end{proof}
